oolong: An R package for validating  automated content analysis tools

### 2020-07-22 paper/paper.rmd
adding rhetorical question, ref #31
cf., ref #31

Validity is a requirement of content analysis [@krippendorff2018content; @neuendorf2016content]. Validation of automated methods has been called for by many scholars, e.g. @grimmer2013text; @ribeiro2016sentibench; @van2018communication. The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other. These three operations are: 1) *statistical* validation --to see if the model results agree with the assumptions of the model. Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model; 2) *semantic* validation --to see if the model results are semantically making sense. This procedure involves comparing model results with human judgment [@grimmer2011general]; 3) *predictive* validation --to see if the model results can predict external events [@quinn2010analyze]. For example, one can study whether external events can explain surges in attention to a topic extracted by a topic model.

@@

Finally, predictive validation is dependent on research questions and thus it is difficult to be generalized as a reusable software framework. Additionally, the relationship between external (sociopolitical) events and the results from automated content analysis tools is usually what social scientists are eager to study, c.f. using topic models for information retrieval [@yi2008evaluating]. We do not believe social scientists would ignore conducting any form of predictive validation.

>>>>

Validity is a requirement of content analysis [@krippendorff2018content; @neuendorf2016content]. Validation of automated methods has been called for by many scholars, e.g. @grimmer2013text; @ribeiro2016sentibench; @van2018communication. But how to validate these methods? The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other. These three operations are: 1) *statistical* validation --to see if the model results agree with the assumptions of the model. Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model; 2) *semantic* validation --to see if the model results are semantically making sense. This procedure involves comparing model results with human judgment [@grimmer2011general]; 3) *predictive* validation --to see if the model results can predict external events [@quinn2010analyze]. For example, one can study whether external events can explain surges in attention to a topic extracted by a topic model.

@@

Finally, predictive validation is dependent on research questions and thus it is difficult to be generalized as a reusable software framework. Additionally, the relationship between external (sociopolitical) events and the results from automated content analysis tools is usually what social scientists are eager to study, cf. using topic models for information retrieval [@yi2008evaluating]. We do not believe social scientists would ignore conducting any form of predictive validation.
